Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks

### 2017-01-03 docs/papers/2016JNCA/2016JNCA.tex
inclusao de trabalhos futuros para atender as consideracoes da revisao R1

In our previous work \cite{tenorio2013greatest}, the accuracy of AIC, MDL, EDC, RADOI, EFT and SURE schemes are evaluated for synflood and port scan attack detection, showing that EDC and EFT are effective for detecting this kind of attacks. The present work extends that evaluation to also analyse the effectiveness of the listed MOS schemes for fraggle attack detection, as shown in Section \ref{sec:experimentalresults}.

@@

Cosine similarity calculates the cosine of the angle between two vectors, which represents the similarity of values between the selected vectors. Therefore, cosine similarity can be used to evaluate the variation of the most significant eigenvectors of $\boldsymbol{V}^{(q)}$ against the the most significant eigenvectors of time frame detected as under attack, to analyse similarity changes into the most significant eigenvectors caused by the insertion of anomalous traffic \cite{Lee2013}.

@@

Future research is directed to improvements for obtaining better false positive rates, as well as for make the proposed framework able to identify sparse probe attacks, considering the evaluation of novel datasets. Additionally, future research can evaluate the application of the proposed approach to different attack types and domains, considering cases that are aware to behavioral analysis.

>>>>

In our previous work \cite{tenorio2013greatest}, the accuracy of AIC, MDL, EDC, RADOI, EFT and SURE schemes are evaluated for synflood and port scan attack detection, showing that EDC and EFT are effective for detecting this kind of attacks. The present work extends that evaluation to also analyze the effectiveness of the listed MOS schemes for fraggle attack detection, as shown in Section \ref{sec:experimentalresults}.

@@

Cosine similarity calculates the cosine of the angle between two vectors, which represents the similarity of values between the selected vectors. Therefore, cosine similarity can be used to evaluate the variation of the most significant eigenvectors of $\boldsymbol{V}^{(q)}$ against the the most significant eigenvectors of time frame detected as under attack, to analyze similarity changes into the most significant eigenvectors caused by the insertion of anomalous traffic \cite{Lee2013}.

@@

Future research is directed to improvements for obtaining better false positive rates, as well as for make the proposed framework able to identify sparse probe attacks or subtle behaviors, such as exfiltration or covert communication, considering the evaluation of a flow-based analysis and novel datasets. Distributed or parallel processing can also be evaluated to analyze the scalability and processing capacity for monitoring high thoughput network traffic. Additionally, future research can evaluate the application of the proposed approach to different attack types and domains, considering cases that are aware to behavioral analysis.
